---
title: "Lab3A_ManyaVivek"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
download.file(url = "https://ndownloader.figshare.com/files/2292169",
              destfile = "data_raw/portal_data_joined.csv")
```

```{r}
surveys <- read.csv("data_raw/portal_data_joined.csv")
```


```{r}
head(surveys)
```

```{r}
str(surveys)
```

# Number of rows and columns 
```{r}
dim(surveys)
```

# Number of rows 
```{r}
nrow(surveys)
```

# Number of columns 
```{r}
ncol(surveys)
```

# First 6 rows
```{r}
head(surveys)
```

# Last 6 rows 
```{r}
tail(surveys)
```

# Column names 
```{r}
names(surveys)
```

# summary statistics of each column 
```{r}
summary(surveys)
```

# first element in the first column of the data frame (as a vector)
```{r}
surveys[1,1]
```

# first element in the sixth column (as a vector)
```{r}
surveys[1,6]
```

# first column of the data frame (as a vector)
```{r}
surveys[ ,1]
```

# first column of the data frame (as a data frame)
```{r}
surveys[1]
```

# first three elements in the 7th column
```{r}
surveys[1:3,7]
```

# the third row of the data frame 
```{r}
surveys[3, ]
```

# equivalent to head surveys 
```{r}
surveys[1:6, ]
```

# CHALLANGE 
1. Row 200 only
```{r}
surveys[200, ]
```
2. Extract last row
```{r}
n_row <- nrow(surveys)
```
```{r}
surveys[n_row, ]
```
3. Extract middle row
```{r}
surveys[n_row/2, ]
```
4. 
```{r}
surveys[-(7:n_row), ]
```

## FACTORS

```{r}
sex <- factor(c("male", "female", "female", "male"))
```

```{r}
levels(sex)
```
```{r}
nlevels(sex)
```

