---
title: "Lab4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
report_03_11_2020 <- 
read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-11-2020.csv")) %>% 
  rename(Country_Region = "Country/Region", Province_State = "Province/State")
```

```{r}
str(report_03_11_2020)
```

```{r}
head(report_03_11_2020)
```

```{r}
library(DT)
datatable(report_03_11_2020)
```

# Exercises (Part 1)

## Question 1:  

```{r}
report_03_13_2020 <-
read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/03-13-2020.csv")) %>% 
  rename(Country_Region = "Country/Region", Province_State = "Province/State")
```

```{r}
str(report_03_13_2020)
```


```{r}
report_09_13_2020 <-
read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-13-2020.csv"))  
```

```{r}
str(report_09_13_2020)
```

## Question 2: 
```{r}
report_03_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarise(Deaths = sum(Deaths))
```

```{r}
report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarise(Deaths = sum(Deaths))
```

## Question 3: .CONFIRMED CASES PER U.S STATE USE

### 03/13/2020
```{r}
filter(report_03_13_2020, Country_Region == "US") %>% 
  group_by(Province_State) %>% 
  summarise(Confirmed = sum(Confirmed))
```

### 09/13/2020
```{r}
filter(report_09_13_2020, Country_Region == "US") %>% 
group_by(Province_State) %>% 
summarise(Confirmed = sum(Confirmed))
```



## Question 4: TOP 10 COUNTRIES OF DEATH

### 03/13/2020
```{r}
report_03_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarise(Deaths = sum(Deaths)) %>% 
  arrange(desc(Deaths)) %>% 
  slice(1:10)
```

### 09/13/2020
```{r}
report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarise(Deaths = sum(Deaths)) %>% 
  arrange(desc(Deaths)) %>% 
  slice(1:10)
```


# ----------------------------------------------------------------------------



```{r}
library(tidyverse)
```


# Exercise (Part 2)

## Question 5

### Graph: 10 countries with the confirmed cases and deaths on 03/13/2020
```{r}
report_03_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarise(Confirmed = sum(Confirmed), Deaths = sum(Deaths), min_deaths = min(Deaths)) %>% 
arrange(desc(min_deaths)) %>% 
slice(1:10)

ggplot(data = report_03_13_2020, mapping = aes(x = Country_Region, y = Deaths)) +
  geom_point() 
  ggplot(data = report_09_13_2020, mapping = aes(x = Country_Region, y = Confirmed)) +
   geom_point()
```


# Graph: 10 countries with the confirmed cases and deaths on 09/13/2020
```{r}
report_09_13_2020 %>% 
  group_by(Country_Region) %>% 
  summarise(Confirmed = sum(Confirmed), Deaths = sum(Deaths), min_deaths = min(Deaths)) %>% 
arrange(desc(min_deaths)) %>% 
slice(1:10)

ggplot(data = report_09_13_2020, mapping = aes(x = Country_Region, y = Deaths)) +
    geom_point()
ggplot(data = report_09_13_2020, mapping = aes(x = Country_Region, y = Confirmed)) +
    geom_point()
```

## Question 6

### 10 states with the most confirmed cases and deaths on 3/13/2020 

#### graph 1: 10 states with the most confirmed cases on 03/13/2020
```{r}
report_03_13_2020 %>%
  filter(Country_Region =="US") %>% 
  group_by(Province_State) %>% 
  summarise(Confirmed) %>% 
  arrange(desc(Confirmed)) %>% 
  slice(1:10) %>% 

ggplot(aes(x = Confirmed,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```

#### graph 2: 10 states with the most deaths on 03/13/2020
```{r, fig.height= 20, fig.width= 10}
report_03_13_2020 %>%
  group_by(Province_State) %>% 
  summarise(Deaths) %>% 
  arrange(desc(Deaths)) %>% 
  slice(1:10) %>% 

ggplot(aes(x = Deaths,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```


### 10 states with the most confirmed cases and deaths on 9/13/2020 

#### graph 1: 10 states with the most confirmed cases on 09/13/2020
```{r, fig.height= 20, fig.width= 10}
report_09_13_2020 %>%
  filter(Country_Region =="US") %>% 
  group_by(Province_State) %>% 
  summarise(Confirmed) %>% 
  arrange(desc(Confirmed)) %>% 
  slice(1:10) %>% 

ggplot(aes(x = Confirmed,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```

#### graph 2: 10 states with the most deaths on 09/13/2020
```{r, fig.height= 20, fig.heigh = 10}
report_09_13_2020 %>%
  filter(Country_Region =="US") %>% 
  group_by(Province_State) %>% 
  summarise(Deaths) %>% 
  arrange(desc(Deaths)) %>% 
  slice(1:10) %>% 

ggplot(aes(x = Deaths,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```