---
title: "Lab5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


# Exercise 2 

## 06/13/2020
```{r}
Confirmed_State_06_13 <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/06-13-2020.csv"))
```


```{r}
Confirmed_State_06_13 <- Confirmed_State_06_13 %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State, Country_Region) %>% 
  summarise(Confirmed = sum(Confirmed))
str(Confirmed_State_06_13)
```

## 09/13/2020
```{r}
Confirmed_State_09_13 <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-13-2020.csv")) %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State, Country_Region) %>% 
  summarise(Confirmed = sum(Confirmed))
str(Confirmed_State_09_13)
```

## Difference of Subsets (06/13/2020 and 09/13/2020)
```{r}
setdiff(Confirmed_State_09_13$Province_State, Confirmed_State_06_13$Province_State)
```

```{r}
Confirmed_State_09_13 <- Confirmed_State_09_13 %>% 
  filter(Province_State != "Recovered") 
```

## Exercise 2 
###Joining Tables from Confirmed cases on 06/13/2020 and 09/13/2020
```{r}
Confirmed_State_6_13_9_13_joined <- full_join(Confirmed_State_06_13,
      Confirmed_State_09_13, by = c("Province_State"))
head(Confirmed_State_6_13_9_13_joined)
```

# Exercise 3: Graph - Joining Tables from Confirmed cases on 06/13/2020 and 09/13/2020
```{r, fig.height = 20, fig.width = 10}
Confirmed_State_6_13_9_13_joined %>%
  ggplot(aes(x = Confirmed.x,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```


# Working with Time Series Data 

# Exercise 4: plot of the total number of confirmed deaths per day worldwide

```{r}
time_series_deaths_long <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")) %>% 
  rename(Province_State = "Province/State", Country_Region = "Country/Region" ) %>% 
    pivot_longer(-c(Province_State, Country_Region, Lat, Long),
                            names_to = "Date", values_to = "Deaths") %>% 
   unite(Key, Province_State, Country_Region, Date, sep = ".") %>% 
  select(Key, Deaths)
head(time_series_deaths_long)
```

```{r}
time_series_confirmed_long <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")) %>%
  rename(Province_State = "Province/State", Country_Region = "Country/Region") %>% 
   pivot_longer(-c(Province_State, Country_Region, Lat, Long),
                            names_to = "Date", values_to = "Confirmed") %>%
    unite(Key, Province_State, Country_Region, Date, sep = ".", remove = FALSE)
head(time_series_confirmed_long)
```

## Full join - common to the tables will be joined 

```{r}
time_series_long_joined <- full_join(time_series_confirmed_long,
              time_series_deaths_long, by = c("Key")) %>% 
              select(-Key)
head(time_series_long_joined)
```

```{r}
library(lubridate)
```

```{r}
time_series_joined_mutate <- time_series_long_joined %>% 
  mutate(Deaths_per_Confirmed = Deaths/Confirmed) %>% 
filter(!is.na(Deaths_per_Confirmed))
head(time_series_joined_mutate)
```

```{r}
time_series_long_joined_counts <- time_series_long_joined %>% 
  pivot_longer(-c(Province_State, Country_Region, Lat, Long, Date),
               names_to = "Report_Type", values_to = "Counts")
head(time_series_long_joined_counts)
```


# Exercise 4: Plot of the total number of confirmed deaths per day worldwide


```{r}
time_series_long_joined %>% 
  group_by(Date) %>% 
    summarise_at(c("Confirmed", "Deaths"), sum) %>% 
    ggplot(aes(x = Date,  y = Deaths)) + 
    geom_point() +
    geom_line() +
    ggtitle("Global COVID-19 Deaths")
```

# Exercise 5:Mutate to make a new column with deaths/confirmed cases

```{r}
time_series_long_joined_mutated <- time_series_long_joined %>% 
  mutate(Deaths_per_Confirmed = Deaths / Confirmed) %>% 
filter(!is.na(Deaths_per_Confirmed))
head(time_series_long_joined_mutated)
```

# Exercise 6: Plot US deaths/confirmed cases per day.

```{r}
time_series_long_confirmed_US <- 
  read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv")) %>% 
  pivot_longer(-c(Province_State, Country_Region, UID, iso2, iso3, code3, FIPS, Lat, Long_, Combined_Key, Admin2),
                            names_to = "Date", values_to = "Confirmed") %>% 
    unite(Key, Province_State, Date, Confirmed, sep = ".", remove = FALSE)
head(time_series_long_confirmed_US)
```


```{r}
time_series_deaths_US <- 
  read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"))
```


```{r}
time_series_long_deaths_US <- time_series_deaths_US %>% 
                 pivot_longer(-c(Province_State, Country_Region, UID, iso2, iso3, code3, FIPS, Lat, Long_, Combined_Key, Admin2, Population),
                            names_to = "Date", values_to = "Deaths") %>% 
    unite(Key, Province_State, Date, sep = ".") %>% 
  select(Key, Deaths)
```

```{r}
time_series_joined_US <- full_join(time_series_long_confirmed_US, time_series_long_deaths_US, by = c("Key")) %>% 
                                     select(-Key)
head(time_series_joined_US)
```

```{r}
time_series_joined_US_mutate <- time_series_joined_US %>% 
  mutate(Deaths_per_Confirmed = Deaths/Confirmed) %>% 
filter(!is.na(Deaths_per_Confirmed))
head(time_series_joined_US_mutate)
```

# EXERCISE 7: TOP 10 COUNTRIES WITH THE HIGHEST DEATH TOTAL 

```{r}
time_series_long_joined_deaths <- time_series_long_joined %>% 
  group_by(Country_Region) %>% 
  summarise(totaldeaths = sum(Deaths)) %>% 
  arrange(desc(totaldeaths)) %>% 
  slice(1:10)
head(time_series_long_joined_deaths)
```

```{r, fig.height = 5, fig.width = 10}
time_series_long_joined %>% 
  group_by(Country_Region,Date) %>% 
  summarise_at(c("Confirmed", "Deaths"), sum) %>% 
  filter(Country_Region %in% c("US","Brazil","United Kingdom", 
                                "Italy", "Mexico" , "France", "Spain", "India", "Iran", "Peru")) %>% 
    ggplot(aes(x = Date,  y = Deaths, color = Country_Region)) + 
    geom_point() +
    geom_line() +
    ggtitle("COVID-19 Deaths")
```


## Facet_Wrap
## Exercise 8 
```{r, fig.height = 20, fig.width = 10}
time_series_long_joined %>% 
  group_by(Country_Region,Date) %>% 
  summarise_at(c("Confirmed", "Deaths"), sum) %>% 
  filter (Country_Region %in% c("US","Brazil","United Kingdom", 
                                "Italy", "Mexico" , "France", "Spain", "India", "Iran", "Peru")) %>% 
    ggplot(aes(x = Date,  y = Deaths)) + 
    geom_point() +
    geom_line() +
    ggtitle("COVID-19 Deaths") +
    facet_wrap(~Country_Region, ncol=2, scales="free_y")
```

## Exercise 9 

```{r}
time_series_joined_US_top10 <- time_series_joined_US %>% 
  group_by(Province_State) %>% 
  summarise(Confirmed = sum(Confirmed)) %>% 
  arrange(desc(Confirmed)) %>% 
  slice(1:10)
```



```{r, fig.height = 10, fig.width = 10}
time_series_joined_US %>% 
  group_by(Province_State,Date) %>% 
  summarise_at(c("Confirmed", "Deaths"), sum) %>% 
  filter (Province_State %in% c("New York","California","Texas", 
                               "Florida", "New Jersey" , "Illinois", "Georgia", "Arizona", "Massachusetts", "Pennsylvania")) %>% 
    ggplot(aes(x = Date,  y = Confirmed)) + 
    geom_point() +
    geom_line() +
    ggtitle("COVID-19 Confirmed cases in the US") +
    facet_wrap(~ Province_State, ncol=2, scales="free_y")
```


