---
title: "Lab5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


# Exercise 2 

## 06/13/2020
```{r}
Confirmed_State_06_13 <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/06-13-2020.csv"))
```


```{r}
Confirmed_State_06_13 <- Confirmed_State_06_13 %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State, Country_Region) %>% 
  summarise(Confirmed = sum(Confirmed))
str(Confirmed_State_06_13)
```

## 09/13/2020
```{r}
Confirmed_State_09_13 <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/09-13-2020.csv")) %>% 
  filter(Country_Region == "US") %>% 
  group_by(Province_State, Country_Region) %>% 
  summarise(Confirmed = sum(Confirmed))
str(Confirmed_State_09_13)
```

## Difference of Subsets (06/13/2020 and 09/13/2020)
```{r}
setdiff(Confirmed_State_09_13$Province_State, Confirmed_State_06_13$Province_State)
```

```{r}
Confirmed_State_09_13 <- Confirmed_State_09_13 %>% 
  filter(Province_State != "Recovered") 
```

## Exercise 2 
###Joining Tables from Confirmed cases on 06/13/2020 and 09/13/2020
```{r}
Confirmed_State_6_13_9_13_joined <- full_join(Confirmed_State_06_13,
      Confirmed_State_09_13, by = c("Province_State"))
head(Confirmed_State_6_13_9_13_joined)
```

### Graph - Joining Tables from Confirmed cases on 06/13/2020 and 09/13/2020
```{r}
Confirmed_State_6_13_9_13_joined %>%
  ggplot(aes(x = Confirmed.x,  y = Province_State)) + 
    geom_bar(stat = 'identity') 
```


# Working with Time Series Data 

Exercise 4 
## Confirmed Deaths 

```{r}
time_series_deaths <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")) %>% 
  rename(Province_State = "Province/State", Country_Region = "Country/Region" )
head(time_series_deaths)
```

```{r}
time_series_deaths_long <- time_series_deaths %>% 
               pivot_longer(-c(Province_State, Country_Region, Lat, Long),
                            names_to = "Date", values_to = "Deaths") 
head(time_series_deaths_long)
```

```{r}
time_series_deaths_long <- time_series_deaths_long %>% 
  unite(Key, Province_State, Country_Region, Date, sep = ".") %>% 
  select(Key, Deaths)
head(time_series_deaths_long)
```

```{r}
time_series_confirmed <- read_csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")) %>%
  rename(Province_State = "Province/State", Country_Region = "Country/Region")
head(time_series_confirmed)
```





```{r}
time_series_confirmed_long <- time_series_confirmed %>% 
               pivot_longer(-c(Province_State, Country_Region, Lat, Long),
                            names_to = "Date", values_to = "Confirmed") 
head(time_series_confirmed_long)
```




```{r}
time_series_confirmed_long <- time_series_confirmed_long %>% 
  unite(Key, Province_State, Country_Region, Date, sep = ".", remove = FALSE)
head(time_series_confirmed_long)
```




## Full join - common to the tables will be joined 

```{r}
time_series_long_joined <- full_join(time_series_confirmed_long,
              time_series_deaths_long, by = c("Key")) %>% 
              select(-Key)
head(time_series_long_joined)
```


```{r}
which(is.na(time_series_long_joined$Confirmed))
```

```{r}
which(is.na(time_series_long_joined$Deaths))
```

```{r}
library(lubridate)
```

```{r}
time_series_long_joined$Date <- mdy(time_series_long_joined$Date)
```

```{r}
time_series_long_joined_counts <- time_series_long_joined %>% 
  pivot_longer(-c(Province_State, Country_Region, Lat, Long, Date),
               names_to = "Report_Type", values_to = "Counts")
head(time_series_long_joined_counts)
```


Exercise 4 
```{r}
time_series_long_joined %>% 
  group_by(Date) %>% 
  summarise_at(c("Deaths"), sum) %>% 
    ggplot(aes(x = Date,  y = Deaths)) + 
    geom_point() +
    geom_line() +
    ggtitle("Global COVID-19 Deaths")
```

Exercise 5 


```{r}
time_series_long_joined_mutated <- time_series_long_joined %>% 
  mutate(Deaths_per_Confirmed = Deaths / Confirmed) %>% 
filter(!is.na(Deaths_per_Confirmed))
head(time_series_long_joined)
```

Exercise 6
Plot US deaths/confirmed cases per day.



```{r}
time_series_long_joined_US <- time_series_long_joined %>% 
  filter(Country_Region == "US") %>% 
  mutate(Deaths_per_Confirmed = Deaths / Confirmed) %>% 
filter(!is.na(Deaths_per_Confirmed))
head(time_series_long_joined_US)
```

```{r}
time_series_long_joined_US %>% 
    ggplot(aes(x = Date,  y = Deaths_per_Confirmed)) + 
    geom_point() +
    geom_line() +
    ggtitle("US COVID-19 Deaths")
```

## EXERCISE 7 
TOP 10 COUNTRIES WITH THE HIGHEST DEATH TOTAL 

```{r}
time_series_long_joined_deaths <- time_series_long_joined %>% 
  group_by(Country_Region) %>% 
  summarise(totaldeaths = sum(Deaths)) %>% 
  arrange(desc(totaldeaths)) %>% 
  slice(1:10)
head(time_series_long_joined_deaths)
```

```{r}
time_series_long_joined %>% 
  group_by(Country_Region,Date) %>% 
  summarise_at(c("Confirmed", "Deaths"), sum) %>% 
  filter(Country_Region %in% c("US","Brazil","United Kingdom", 
                                "Italy", "Mexico" , "France", "Spain", "India", "Iran", "Peru")) %>% 
    ggplot(aes(x = Date,  y = Deaths, color = Country_Region)) + 
    geom_point() +
    geom_line() +
    ggtitle("COVID-19 Deaths")
```


## Facet_Wrap
## Exercise 8 
```{r}
time_series_long_joined %>% 
  group_by(Country_Region,Date) %>% 
  summarise_at(c("Confirmed", "Deaths"), sum) %>% 
  filter (Country_Region %in% c("US","Brazil","United Kingdom", 
                                "Italy", "Mexico" , "France", "Spain", "India", "Iran", "Peru")) %>% 
    ggplot(aes(x = Date,  y = Deaths)) + 
    geom_point() +
    geom_line() +
    ggtitle("COVID-19 Deaths") +
    facet_wrap(~Country_Region, ncol=2, scales="free_y")
```

## Exercise 9 
```{r}
time_series_long_joined %>% 
  group_by(Country_Region,Date) %>% 
  summarise_at(c("Confirmed", "Deaths"), sum) %>% 
  filter (Country_Region %in% c("US","Brazil","United Kingdom", 
                                "Italy", "Mexico" , "France", "Spain", "India", "Iran", "Peru")) %>% 
    ggplot(aes(x = Date,  y = Confirmed)) + 
    geom_point() +
    geom_line() +
    ggtitle("COVID-19 Confirmed Cases") +
    facet_wrap(~Country_Region, ncol=2, scales="free_y")
```

