---
title: "Lab 9"
author: "Manya Vivek"
date: "10/26/2020"
output: html_document
---

# 14.3.1 BASIC MATCHES
```{r}
library(stringr)
library(tidyverse)
```

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "an")
```


```{r}
# the dot mataches any character
str_view(x, ".a.")
str_view(x, "..a")
```


```{r}
# how do you match the character “.”? 
# To create the regular expression, we need \\
dot <- "\\."

# But the expression itself only contains one:
writeLines(dot)
```

```{r}
# And this tells R to look for an explicit .
x <- c("abc", "a.c", "bef")
str_view(x, "a\\.c")

```

```{r}
y <- c("ab.cd", "b.c", "c.def")
str_view(y, "b\\.c")
```

```{r}
# to create regular expression "\", we need the string "\\" 
dot <- "\\"
writeLines(dot)
```

```{r}
# to create regular expression "\", we need the string "\\" 
dot <- "\\."
writeLines(dot)
```
```{r}
x <- c("abc", "a.c", "bef")
str_view(x, "a.c")
```
\\
```{r}
x <- c("abc", "a.c", "bef")
str_view(x, "a\\.c")
```

```{r}
# to create the regular expression "\" we need the string "\\".
x <- "a\\b"
writeLines(x)
```

```{r}
str_view(x, "\\\\")
```


### 14.3.1 Exercises

1. i. "\\" -> escape a character or symbol in strings. 
  ii. "\\\\" -> Unrecognized backslash escape sequence in pattern
  iii. "\\\\\\\" -> escape the next character. 

2. 
```{r}
x <- "\"'\\"
writeLines(x)
```

```{r}
x <- ("\"'\\")
str_view(x, "\"'\\\\")
```


3. 
```{r}
# "\." matches a dot and "." matches any character
y <- (".l.o.l")
str_view(y , "\\..\\..\\..")
```

# 14.3.2 ANCHORS

```{r}
# "^" to match the start of the string.
# $ to match the end of the string.
x <- c("apple", "mango", "banana", "avacado")
str_view(x, "^a")
str_view(x, "a$")
```

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "^a")
```

```{r}
x <- c("apple pie", "apple", "apple cake", "green apple")
str_view(x, "apple")
```
```{r}
# To force a regular expression to only match a complete string, anchor it with both "^" and "$"
str_view(x, "^apple$")
```

### 14.3.2 Exercises

1. 
```{r}
str_view(c("$^$", "abc$^$abc"), "^\\$\\^\\$$")
```
2. 
(i)
```{r}
x <- c("yell","youth","fax","tax")
str_view(x, "^y")
```
```{r}
str_view(stringr::words, "^y", match = TRUE)
```

(ii)

```{r}
str_view(stringr::words, "x$", match = TRUE)
```

(iii)
```{r}
# "." represents characters
# only three letters therefore, both "^" and "$" needs to be used 
str_view(stringr::words, "^...$", match = TRUE)
```
(iv)
```{r}
# seven letter or more
str_view(stringr::words, "^.......", match = TRUE)
```

# 14.3.3 Character classes and alternatives

##### * "\\d" : matches any digit.
##### * "\\s" : matches any whitespace (e.g. space, tab, newline).
##### * [abc] : matches a, b, or c.
##### * [^abc] : matches anything except a, b, or c.

```{r}
x <- c("abc", "a.c", "a*c", "a c")
str_view(x, "a[.]c")
str_view(x, ".[*]c")
str_view(x, "a[ ].")
```
```{r}
x <- c("grey", "gray")
str_view(x, "gr(e|a)y")
```
### 14.3.3 Exercises

1. 
```{r}
str_view(stringr::words, "^[aeiou]")
```

```{r}
str_subset(stringr::words, "[aeiou]", negate=TRUE)
```


```{r}
str_view(stringr::words, "[aeiou]", match=FALSE)
```

```{r}
str_subset(c("ed", stringr::words), "(^|[^e])ed$")
```

```{r}
# ending in ing or ise
str_view(stringr::words, "i(ng|se)$", match = TRUE)
```

2. cie 
```{r}
str_subset(stringr::words, "(cie|[^c])ie")
```
3. 
```{r}
# is "q" always followed by "u"
str_subset(stringr::words, "q[^u]" )
```
4. Write a regular expression that matches a word if it’s probably written in British English, not American English.
o <- ou
ise <- ize 
a <- ae
o <- oe

```{r}
str_subset(stringr::words, "ou|ise$|ae|oe" )
```


5. 

# 14.3.4 Repetition

```{r}
x <- c("123-456-7890", "(123)456-7890", "(123) 456-7890", "1235-2351")
str_view(x, "\\d\\d\\d-\\d\\d\\d-\\d\\d\\d\\d")
```

```{r}
x <- "1888 is the longest year in Roman numerals: MDCCCLXXXVIII"
str_view(x, "CC?")
str_view(x, "CC+")
str_view(x, 'C[LX]+')
```

```{r}
str_view(x, "C{2}")
str_view(x, "C{2,}")
str_view(x, 'C{2,3}?')
str_view(x, 'C[LX]+?')
```

# 14.3.4 Exercise 

1. 
? <- (0,1)
+ <- (1,)
* <- (0,)

2. 
(1) ^.*$ - match any string
(2) "\\\\{.+\\\\}" - match any string with curly braces surrounding at least one character.
(3) \\d{4}-\\d{2}-\\d{2} - will match four digits followed by a hyphen, followed by two digits followed by a hyphen, followed by another two digits
"\\\\\\\\{4}" - is \\\\{4}, which will match four backslashes. 

3. 
* 
```{r}
str_view(words, "^[^aeiou]{3}", match = TRUE)
```

```{r}
str_view(words, "[aeiou]{3,}", match = TRUE)
```

```{r}
str_view(words, "([aeiou][^aeiou]){2,}", match = TRUE)
```


# 14.3.5 Grouping and backreferences

```{r}
str_view(fruit, "(..)\\1", match = TRUE)
```

(.)\\1\\ <- 1same letter appearing three times consequtively 
(.)(.)\\\\2\\\\1 <- it is read the same foward and in reverse ex: eppe in pepper 
(..)\\1 <- any two letters repeated
(.).\\\\1.\\\\1 <-  A letter followed by any letter, the original letter, any other letter, the original letter again
"(.)(.)(.).*\\\\3\\\\2\\\\1"<- three characters followed by zero or more characters of any kind followed by the same three characters but in reverse order.

```{r}
str_subset(words, "^(.)((.*\\1$)|\\1?$)")
```

```{r}
str_subset("remember", "([A-Za-z][A-Za-z]).*\\1")
```

```{r}
str_subset(words, "([A-Za-z][A-Za-z]).*\\1")
```

```{r}
str_subset("eleven", "([a-z]).*\\1.*\\1")
```
```{r}
str_subset(words, "([a-z]).*\\1.*\\1")
```

# 14.4 Tools

```{r}
x <- c("apple", "banana", "pear")
str_detect(x, "e")
```

```{r}
# How many common words start with t?
sum(str_detect(words, "^t"))
```

```{r}
# What proportion of common words end with a vowel?
mean(str_detect(words, "[aeiou]$"))
```

```{r}
# Find all words containing at least one vowel, and negate
no_vowels_1 <- !str_detect(words, "[aeiou]")
```

```{r}
# Find all words consisting only of consonants (non-vowels)
no_vowels_2 <- str_detect(words, "^[^aeiou]+$")
identical(no_vowels_1, no_vowels_2)
```

```{r}
words[str_detect(words, "x$")]
```

```{r}
str_subset(words, "x$")
```

```{r}
df <- tibble(
  word = words, 
  i = seq_along(word)
)
df %>% 
  filter(str_detect(word, "x$"))
```

```{r}
x <- c("apple", "banana", "pear")
str_count(x, "a")
```

```{r}
mean(str_count(words, "[aeiou]"))
```

```{r}
df %>% 
  mutate(
    vowels = str_count(word, "[aeiou]"),
    consonants = str_count(word, "[^aeiou]")
  )
```

```{r}
str_count("abababa", "aba")
```

```{r}
str_view_all("abababa", "aba")
```

### 14.4.1.1 Exercises

For each of the following challenges, try solving it by using both a single regular expression, and a combination of multiple str_detect() calls.
Find all words that start or end with x.
Find all words that start with a vowel and end with a consonant.
Are there any words that contain at least one of each different vowel?
What word has the highest number of vowels? What word has the highest proportion of vowels? (Hint: what is the denominator?)

# 14.4.2 Extract matches

```{r}
length(sentences)
```

```{r}
head(sentences)
```

```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match <- str_c(colours, collapse = "|")
colour_match
```

```{r}
has_colour <- str_subset(sentences, colour_match)
matches <- str_extract(has_colour, colour_match)
head(matches)
```

```{r}
has_colour
```

```{r}
more <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more, colour_match)
```
```{r}
str_extract(more, colour_match)
```

```{r}
str_extract_all(more, colour_match)
```

```{r}
str_extract_all(more, colour_match, simplify = TRUE)
```

```{r}
x <- c("a", "a b", "a b c")
str_extract_all(x, "[a-z]", simplify = TRUE)
```

```{r}
noun <- "(a|the) ([^ ]+)"

has_noun <- sentences %>%
  str_subset(noun) %>%
  head(10)
has_noun %>% 
  str_extract(noun)
```

```{r}
has_noun %>% 
  str_match(noun)
```
```{r}
tibble(sentence = sentences) %>% 
  tidyr::extract(
    sentence, c("article", "noun"), "(a|the) ([^ ]+)", 
    remove = FALSE
  )
```
### 14.4.3.1 Exercises

Find all words that come after a “number” like “one”, “two”, “three” etc. Pull out both the number and the word.
Find all contractions. Separate out the pieces before and after the apostrophe.

```{r}

```

# 14.4.4 Replacing matches

```{r}
x <- c("apple", "pear", "banana")
str_replace(x, "[aeiou]", "-")
```

```{r}
str_replace_all(x, "[aeiou]", "-")
```

```{r}
x <- c("1 house", "2 cars", "3 people")
str_replace_all(x, c("1" = "one", "2" = "two", "3" = "three"))
```

```{r}
sentences %>% 
  str_replace("([^ ]+) ([^ ]+) ([^ ]+)", "\\1 \\3 \\2") %>% 
  head(5)
```

# 14.4.5 Splitting

```{r}
sentences %>%
  head(5) %>% 
  str_split(" ")
```

```{r}
"a|b|c|d" %>% 
  str_split("\\|") %>% 
  .[[1]]
```

```{r}
sentences %>%
  head(5) %>% 
  str_split(" ", simplify = TRUE)
```

```{r}
fields <- c("Name: Hadley", "Country: NZ", "Age: 35")
fields %>% str_split(": ", n = 2, simplify = TRUE)
```

```{r}
x <- "This is a sentence.  This is another sentence."
str_view_all(x, boundary("word"))
```

```{r}
str_split(x, " ")[[1]]
```

```{r}
str_split(x, boundary("word"))[[1]]
```

